testibng

### 2024-01-07 Code/R FIle.qmd
combined state data

```{r}
summary(wages)
```

@@

```{r}
summary(states)
```

@@

```{r}
house <- house |>
  mutate(state = str_to_sentence(state)) |> # change from all caps to sentence case) 
  select(!(state_fips:office)) |> #Remove unwanted columns
  select(!(stage:candidate)) |> 
  select(!(writein:fusion_ticket)) 
```

@@

```{r}
union_states <- union_states |> 
  select(-state_census_code,
         -observations) |> 
  mutate(employment_count = employment * 1000, .keep = "unused") |> 
  mutate(union_employment_count = members * 1000, .keep = "unused") |> 
  mutate(collective_bargaion_employment_count = covered * 1000, .keep = "unused") |> 
  rename(
    percent_union = p_members,
    percent_collective_bargain = p_covered
  )
```

@@

#### Combining house and states dataframes

@@

```{r}
test <- minimum_wage
```

```{r}
full_data <- union_states |> 
  filter(sector == "Total") |> 
  left_join(house, by = c("year", "state")) |> 
  filter(party == "DEMOCRAT" | party == "REPUBLICAN") |> 
  mutate(decade = paste0((year - year %% 10), "s"),
         party_binary = ifelse(party == "DEMOCRAT", 0, 1))  |> 
  seelect 
```

@@

```{r}
full_data |> 
  ggplot(aes(x = year, y = p_covered, color = regions)) +
  geom_point() +
  geom_smooth()
```

```{r}
full_data |> 
  ggplot(aes(x = party, y = p_members)) +
  geom_boxplot() +
  facet_wrap(vars(decade))
```

```{r}
t.test(p_members ~ party, data = full_data, conf.level = .9)
```

```{r}
full_data_after_2008 <- full_data |> 
  filter(year > 2008)
t.test(p_members ~ party, data = full_data_after_2008, conf.level = .9)
```

@@

```{r}
model <- glm(party_binary ~ p_members, family = "binomial", data = full_data)
summary(model)
```

>>>>

```{r}
summary(union_wages)
```

@@

```{r}
summary(union_states)
```

@@

```{r}
house <- house |>
  group_by(year, state, district) |> 
  filter(candidatevotes == max(candidatevotes)) |> 
  ungroup() |> 
  mutate(state = str_to_sentence(state)) |> # change from all caps to sentence case) 
  select(!(state_fips:office)) |> #Remove unwanted columns
  select(!(stage:candidate)) |> 
  select(!(writein:fusion_ticket)) |> 
  rename(state_abbreviation = state_po)
```

@@

```{r}
union_states <- union_states |> 
  select(-state_census_code,
         -observations) |> 
  mutate(employment_count = employment * 1000, .keep = "unused") |> 
  mutate(union_employment_count = members * 1000, .keep = "unused") |> 
  mutate(collective_bargain_employment_count = covered * 1000, .keep = "unused") |> 
  rename(
    percent_union = p_members,
    percent_collective_bargain = p_covered
  )
```

@@

```{r}
head(union_wages)
head(union_states)
head(house)
head(income_distribution)
head(minimum_wage)
```
```{r}
range(union_wages$year) #ntl
range(union_states$year) # state
range(house$year) # state
range(income_distribution$year) # ntl
range(minimum_wage$year) # state
```

### Combining dataframes

@@

#### State Dataframes
```{r}
full_state_data <- union_states |> 
  filter(sector == "Total") |> 
  select(-sector,
         -state_abbreviation) |> 
  left_join(house, by = c("year", "state")) |> 
  filter(party == "DEMOCRAT" | party == "REPUBLICAN") |> 
  mutate(decade = paste0((year - year %% 10), "s"),
         party_binary = ifelse(party == "DEMOCRAT", 1, 0)) |> 
  left_join(minimum_wage, by = c("year", "state")) |> 
  group_by(year, state) |> 
  mutate(party_state_avaerage = mean(party_binary))
```

```{r}
state_column_list = c("year", "decade", "state", "state_abbreviation",
                      "regions", "district", "party", "party_binary",
                      "employment_count", "union_employment_count",
                      "collective_bargain_employment_count", "percent_union",
                      "percent_collective_bargain", "state_min_wage",
                      "state_min_wage_2020_adj", "fed_min_wage",
                      "fed_min_wage_2020_adj", "effective_min_wage",
                      "effective_min_wage_2020_adj", "CPI_avg")
full_state_data <- full_state_data[, state_column_list]
```

```{r}
range(full_state_data$year)
```

@@

@@
